\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\renewcommand\bibname{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\begin{thebibliography}{}
	
	\setlength\bibindent{1.25cm}
	\makeatletter
	\let\old@biblabel\@biblabel
	\def\@biblabel#1{\kern\bibindent\old@biblabel{#1}}
	\makeatother
	
	\bibitem{recursive} Combining Convolutional Neural Network With Recursive Neural Network for Blood Cell Image Classification [Электронный ресурс]. URL: \url{https://ieeexplore.ieee.org/document/8402091} (дата обращения: 25.11.2024).
	
	\bibitem{lightweight} Lightweight CNN Architecture for Software Defect Feature Identification [Электронный ресурс]. URL:\url{ https://ieeexplore.ieee.org/document/10499820} (дата обращения: 25.11.2024).
	
	\bibitem{survey} A Survey of Convolutional Neural Networks: Analysis, Applications, and Prospects [Электронный ресурс]. URL:\url{https://ieeexplore.ieee.org/document/9451544} (дата обращения: 27.11.2024).
	
	\bibitem{mitcnnchapter} Convolutional Neural Networks [Электронный ресурс]. URL:\url{https://introml.mit.edu/_static/fall22/LectureNotes/chapter_Convolutional_Neural_Networks.pdf} (дата обращения: 27.11.2024).
	
	\bibitem{sparsecnn} Super Sparse Convolutional Neural Networks [Электронный ресурс]. URL:\url{https://ojs.aaai.org/index.php/AAAI/article/view/4356} (дата обращения: 27.11.2024).
	
	\bibitem{understanding} Understanding of a convolutional neural network
	[Электронный ресурс]. URL:\url{https://ieeexplore.ieee.org/document/8308186} (дата обращения: 27.11.2024).
	
	\bibitem{caltech101} High Performance Classification of Caltech-101 with a Transfer Learned Deep Convolutional Neural Network
	[Электронный ресурс]. URL:\url{https://ieeexplore.ieee.org/document/9396917} (дата обращения: 27.11.2024).
	
	\bibitem{berkeley} Understanding and Designing Convolutional Networks for Local Recognition
	Problems [Электронный ресурс]. URL:\url{https://www2.eecs.berkeley.edu/Pubs/TechRpts/2016/EECS-2016-97.pdf} (дата обращения: 27.11.2024).
	
	\bibitem{fullycnnstruct} Fully Convolutional Neural Network Structure and Its Loss Function for Image Classification
	Problems [Электронный ресурс]. URL:\url{https://ieeexplore.ieee.org/document/9745570} (дата обращения: 27.11.2024).
	
	\bibitem{3dimension} Hierarchical Graph Attention Based Multi-View Convolutional Neural Network for 3D Object Recognition [Электронный ресурс]. URL:\url{https://ieeexplore.ieee.org/document/9355182} (дата обращения: 27.11.2024).
	
\end{thebibliography}